30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex
Changed some weird sentence structure in the introduction

\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	% You must have at least 2 lines in the paragraph with the drop letter
	% (should never be an issue)
	\IEEEPARstart{L}{orem} ipsum dolor sit amet, consectetur adipiscing elit. Nunc et elit nec metus ultrices faucibus. Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar. Sed et ipsum nunc. Quisque ac sem ut nunc tincidunt commodo. Cras at odio nibh. Pellentesque sodales ut tortor sed dictum. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.

@@

\section{Problems when decentralizing}
		As we saw in the previous section, we would like to have a decentralized anonymous network. This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us. Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry. These networks will be described in more detail in the next chapter. Among these networks are some overlay anonymous networks such as Tarzan.

		There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users. When removing this central authority, these components needs to be spread across the peers in the network. In this section we will explain the various problems that are involved when decentralizing Tor. In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.

@@

		In the last section, we discussedexisting decentralized peer-to-peer networks. In this section we will make a comparison between these networks. For each network, we will explain the following features:
\begin{itemize}
\item Compatibility with Tor. If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
\item Public implementation. For each network we will explain whether a public implementation is available.
\item Used in practice. Is the network used in practice?
\item Attack resistance. We will explain the various weaknesses and possible attacks of each network.
\end{itemize}

>>>>

\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	% You must have at least 2 lines in the paragraph with the drop letter
	% (should never be an issue)
	\IEEEPARstart{W}{ith} the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate. In many cases however, internet usage is either censored or monitored by third parties. In recent years the need for anonymous internet communication has become more apparent. Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.

	Although much research has been done about anonymous internet communication, only few systems have been actually implemented and used in practice. One of the most important factors that impact anonymity in a communication system is the number of users. A sufficiently large numbers of users are required for the system to make guarantees about its ability to conceal and hide users' communication. This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users. Another important factor is for the system to be decentralized. Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.

	The most widely used anonymous communication system is TOR. In this paper we will analyze TOR and its semi centralized nature. Furthermore we will look at attempts that have been made to decentralize TOR as well as several other decentralized systems.

	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview about Tor. After that we will talk about decentralization and its problems in section \ref{sec:problems}. Vulnerabilities in Tor are discussed in section \ref{sec:attacks}. Afterwards, we will discuss the current state of decentralized internet systems in section \ref{sec:decentralized}. A comparison of existing decentralized networks is made in section \ref{sec:comparison}. Finally we will conclude and discuss our findings in section \ref{sec:conclusion}.

@@

\section{Problems when decentralizing}
		hier komt de introductie

@@

		\subsection{Comparison and differences}
			Comparison table.
